Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-05-01 paper/paper7/paper7.tex
introduction

The social, behavioural, and economic sciences (\emph{SBE}) require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
an XML format to disseminate, manage,
and reuse data collected and archived for research \cite{Vardigan2008}. 
%DDI is heavily used by the CESSDA community of European national data archives, 
%the International Household Survey Network community (made up of more than 90 statistical agencies),
%and ICPSR - the largest SBE data archive in the US.

In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.

With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration. Therefore, not only established vocabularies like \emph{SKOS} are used; 
recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

@@

Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}. It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.

The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts. All in all, this lead to 246 constraints  of 53 different types on six vocabularies. \tb{in total 82 constraint types}
We let the experts classify the constraints according to the severity if they are violated. Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain, range, and cardinality restrictions), 
over types that are simply stated using common constraint languages (e.g., language tag cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible 
%(e.g., constraints on network topologies)
(e.g., constraints on graph-based structures}).

As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.

%The \textbf{contribution} of this paper is the development of a system 
%\begin{enumerate}
	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
%\end{enumerate}
%By defining a huge amount of constraints of the majority of the constraint types,   
%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
%how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding 
%(1) which sets of constraint types (on different levels of complexity) and 
%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).

In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
The remainder of the paper is structured as follows.

@@

\subsection{Motivation}
\label{motivation}

>>>>

The social, behavioural, and economic sciences (\emph{SBE}) require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
an XML format to disseminate, manage,
and reuse data collected and archived for research \cite{Vardigan2008}. 
%DDI is heavily used by the CESSDA community of European national data archives, 
%the International Household Survey Network community (made up of more than 90 statistical agencies),
%and ICPSR - the largest SBE data archive in the US.
In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration. Therefore, not only established vocabularies like \emph{SKOS} are used; 
recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

@@

Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}. It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. 
We distinguish 82 requirements to formulate RDF constraints; 
each of them corresponding to an RDF constraint type.

To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts. All in all, this lead to 246 constraints  of 53 different types on six vocabularies. 
We let the experts classify the constraints according to the severity if they are violated. Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain, range, and cardinality restrictions), 
over types that are simply stated using common constraint languages (e.g., language tag cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible 
%(e.g., constraints on network topologies)
(e.g., constraints on graph-based structures) (section \ref{classification}).

As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
Based on the evaluation results,
we formulated several hypotheses to direct the further development of constraint languages.
To make valid general statements for all vocabularies, however,
the hypotheses still have to be verified or falsified
by evaluating the quality of data represented by more than three vocabularies (section \ref{evaluation}).
%The \textbf{contribution} of this paper is the development of a system 
%\begin{enumerate}
	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
%\end{enumerate}
%By defining a huge amount of constraints of the majority of the constraint types,   
%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
%how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding 
%(1) which sets of constraint types (on different levels of complexity) and 
%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
In this paper, we discuss constraints on RDF data in general. Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data. We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
%The remainder of the paper is structured as follows.

@@
